DeepSphere: a graph-based spherical CNN

### 2019-09-17 main.tex
Updates from Overleaf

\usepackage{hyperref}
\usepackage{url}
\usepackage{breqn}
\usepackage{booktabs}
\usepackage{graphicx} \graphicspath{{figures/}}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}{Proposition}
\newtheorem*{remark}{Remark}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}

@@

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}
\newcommand{\todo}[1]{{\color[rgb]{.6,.1,.6}{#1}}}

@@

\section{Rotation equivariance [2.5 pages]}

\subsection{Link with the Laplace-Beltrami Operator}

\subsection{HEALPix: convergence theorem}

@@

\subsection{Equiangular}

@@

\begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{4}{c}{Accuracy} & Size\\
        \cmidrule(lr){2-5} \cmidrule(lr){6-6}
        \multicolumn{1}{l}{Method} & TC & AR & BG & mean & params \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        \cite{jiang_spherical_2019} & 94 & 93 & 97 & 94.67 & 330k\\
        \cite{jiang_spherical_2019} \emph{rerun} & 93.9 & 95.7 & 95.2 & 94.95 & 330k\\
        % 328'339
        \cite{cohen_gauge_2019} (S2R) & 97.3 & 97.3 & 97.8 & 97.5 & -\\
        \cite{cohen_gauge_2019} (R2R) & 97.8 & 97.4 & 97.9 & 97.7 & -\\ \hline
        DS (weighted) & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $98.2\pm 0.5$ & $97.8\pm 0.3$ & 13M\\
        DS (non-weighted) & $69.2\pm 3.7$ & $94.5\pm 2.9$ & $99.7\pm 0.1$ & $87.8\pm 0.5$ & 13M\\ \hline
        % 12'926'432
        DS-Jiang (weighted) & 97.1 & 97.6 & 96.5 & 97.1 & 590k\\
        DS-Jiang (non-weighted) & 33.6 & 93.6 & 99.3 & 75.5 & 590k\\ \hline
        % 590k
        DS-optimal (non-weighted) & 99.8 & 73.4 & 92.7 & 88.7 & \\ \hline
        %DS-Cohen (weighted) &
        % DeepSphere (equi non-weighted) & 99.9 & 31.3 & 75.2 & 68.80
    \end{tabular}
    \caption{Climate pattern segmentation accuracy (\%) for BG, TC
and AR classes plus mean accuracy.}
\end{table}

@@

\begin{table}
\begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{3}{c}{Average Precision} & \multicolumn{2}{c}{Speed}\\
        \cmidrule(lr){2-4}\cmidrule(lr){5-6}
        \multicolumn{1}{l}{Method} & TC & AR & mean & inference [ms] & training \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        \cite{jiang_spherical_2019} \emph{rerun} & 11.08 & 65.21 & 38.41 & 10.2 & 10h14m\\
        % 328'339
        \cite{cohen_gauge_2019} (S2R) & - & -& 68.6 & - & - \\
        \cite{cohen_gauge_2019} (R2R) & - & -& 75.9 & - & -\\ \hline
        DS (weighted) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ & 33 & 13h \\
        DS (non-weighted) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ & 33 & 13h \\ \hline
        % 12'926'432
        DS-Jiang (weighted) & 49.7 & 89.2 & 69.5 & 5 & 3h06m\\
        DS-Jiang (non-weighted) & 46.2 & 93.9 & 70.0 & 5 & 3h04m \\ \hline
        % 590k
        DS-optimal (non-weighted) & 84.71 & 98.05 & 91.38 & 55 & 22h \\
        % DeepSphere (equi non-weighted) & 55.53 & 94.85 & 75.19 & 567 ms & 48h
    \end{tabular}
    \caption{Climate pattern segmentation average precision for positive classes and mean as well, plus speed performance for inference (one training pass for one instance)  and training time.}
\end{table}

>>>>

\usepackage{hyperref}
\usepackage{url}
\usepackage{breqn}
\usepackage{booktabs}
\usepackage{bbm}        % for mathbbm
\usepackage{graphicx} \graphicspath{{figures/}}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}{Proposition}
\newtheorem*{remark}{Remark}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}

@@

\renewcommand{\b}[1]{{\bm{#1}}}   % bold symbol

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}
\newcommand{\todo}[1]{{\color[rgb]{.6,.1,.6}{#1}}}
\newcommand{\nati}[1]{{\color[rgb]{.3,.5,.9}{#1}}}

@@

\section{Is graph convolution equivariant to rotation? [2 pages]}

% The plan for this section
% 0) Explain why the Laplacian is so important...
By definition, the graph convolution (on the sphere) is rotation equivariant to rotation, if and only if, it commutes with the rotation operator. 
As, in the context of this work, graph convolution can be performed is performed by successive application of the graph Laplacian, i.e: $g(\b{L}) \b{f} = \left(\sum_{i=0}^K \alpha_i \b{L}^i\right) \b{f}$, if the graph Laplacian $\b{L}$ commutes with the rotation operator, then, by recursion, it will also commute with the convolution $g(\b{L})$.
Hence to simplify our analysis, we concentrate on the graph Laplacian.

% 0.5) Explain the sampling and metric
We first need to deal with the sampling problem. The rotation operator $R_{b}$ \nati{define rotation} act on the continuous signal $R(b), b\in SO(3): R(b)f(\omega) = f(g^{-1}\omega)$
graph laplacian on a discrete graph that is build from a sampling.
So we need a sampling operator, ideally invertible. \nati{Define sampling}
Eventually, we formulate the commute error of the graph Laplacian and the rotation operator as: 
equ...
Of course result will depend on the sampling and on the graph construction

% !) summary the work of Khasanova

% 2) explain our approach
Our approach is different as we do not miminize eq... Instead we inspire ourselves with Belkin, which says that for \emph{uniform sampling} the graph Laplacian converges toward the Laplace-Beltrami. b) The Laplace Beltrami commute with rotation.
The following theorem extend the work of Belkin and Niogi to fixed sampling \nati{(Including Healpix or not?)}
THEOREM HERE
This is \emph{not} a proof of equivariance of the graph convolution for a specific sampling. We simply observe that the graph Laplacian converges pointwisely toward an operator that commutes with rotation. To have the desired equality in eq..., we would need to prove a stronger result, for example uniform convergence (in the space of the operators).
\nati{Should we put this here?: }This does not hold in general \cite{belkin-spectral}. However, we believe that this is achievable for a bandlimited signals.
More importantly, the proof of ... in Appendix ... inspires us in the construction of our graph Laplacian. a) use gaussian kernel b) we need to adjust t with respect of n such that ...

% 3) Show experimental results
Define the error, show results and comments

Explain the difference of errors... Uniform sampling is better

\subsection{Theoretical evidence of equivariance}

% \subsection{Equiangular}

\paragraph{Link with the Laplace-Beltrami Operator}

@@

@@

\begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{4}{c}{Accuracy} & Size\\
        \cmidrule(lr){2-5} \cmidrule(lr){6-6}
        \multicolumn{1}{l}{Method} & TC & AR & BG & mean & params \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        \cite{jiang_spherical_2019} & 94 & 93 & 97 & 94.67 & 330k\\
        \cite{jiang_spherical_2019} \emph{rerun} & 93.9 & 95.7 & 95.2 & 94.95 & 330k\\
        % 328'339
        \cite{cohen_gauge_2019} (S2R) & 97.3 & 97.3 & 97.8 & 97.5 & -\\
        \cite{cohen_gauge_2019} (R2R) & 97.8 & 97.4 & 97.9 & 97.7 & -\\ \hline
        DS (weighted) & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $98.2\pm 0.5$ & $97.8\pm 0.3$ & 13M\\
        DS (non-weighted) & $69.2\pm 3.7$ & $94.5\pm 2.9$ & $99.7\pm 0.1$ & $87.8\pm 0.5$ & 13M\\ \hline
        % 12'926'432
        DS-Jiang (weighted) & 97.1 & 97.6 & 96.5 & 97.1 & 590k\\
        DS-Jiang (non-weighted) & 33.6 & 93.6 & 99.3 & 75.5 & 590k\\ \hline
        % 590k
        DS-optimal (weighted) & 91.5 & 93.4 & 99.0 & 94.6 & 52M\\
        DS-optimal (non-weighted) & 73.4 & 92.7 & 99.8 & 88.7 & 52M\\ \hline
        %DS-Cohen (weighted) & 95.5 & 96.9 & 93.9 & 95.4 & 2M \\
        %DS-Cohen (non-weighted) & 95.5 & 96.9 & 93.9 & 95.4 & 2M \\
        % DeepSphere (equi non-weighted) & 31.3 & 75.2 & 99.9 & 68.80
    \end{tabular}
    \caption{Climate pattern segmentation accuracy (\%) for BG, TC
and AR classes plus mean accuracy.}
\end{table}

@@

\begin{table}
\begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{3}{c}{Average Precision} & \multicolumn{2}{c}{Speed}\\
        \cmidrule(lr){2-4}\cmidrule(lr){5-6}
        \multicolumn{1}{l}{Method} & TC & AR & mean & inference [ms] & training \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        \cite{jiang_spherical_2019} \emph{rerun} & 11.08 & 65.21 & 38.41 & 10.2 & 10h14m\\
        % 328'339
        \cite{cohen_gauge_2019} (S2R) & - & -& 68.6 & - & - \\
        \cite{cohen_gauge_2019} (R2R) & - & -& 75.9 & - & -\\ \hline
        DS (weighted) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ & 33 & 13h \\
        DS (non-weighted) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ & 33 & 13h \\ \hline
        % 12'926'432
        DS-Jiang (weighted) & 49.7 & 89.2 & 69.5 & 5 & 3h06m\\
        DS-Jiang (non-weighted) & 46.2 & 93.9 & 70.0 & 5 & 3h04m \\ \hline
        % 590k
        DS-optimal (weighted) & 52.80 & 94.78 & 73.79 & 50 & 20h \\
        DS-optimal (non-weighted) & 84.71 & 98.05 & 91.38 & 50 & 20h \\ \hline
        %DS-Cohen (weighted) & 13.1 & 80.3 & 46.7 & 11 & 4h \\
        % DeepSphere (equi non-weighted) & 55.53 & 94.85 & 75.19 & 567 ms & 48h
    \end{tabular}
    \caption{Climate pattern segmentation average precision for positive classes and mean as well, plus speed performance for inference (one training pass for one instance)  and training time.}
\end{table}
